Physics-informed machine learning of reduced-order model

### 2020-06-24 manuscript/elsarticle/manuscript.tex
pc

%% main text
\section{Introduction}
Why we need reduced-order modeling.

Intrusive reduced-order model. POD-G is a classical choice. Pros and cons.

Intrusive reduced-order model. POD-NN is a recently developed one. Pros and cons. Especially the need of large amount of data for training.

We propose to use physics-informed machine learning to improve the reduced-order modeling by taking advantage of both physics and data. Then explain the idea.

The advantage of PINN over POD-G and POD-NN. Numerical results demonstrate the advantages.

The remainder of this paper is organized as follows.

\section{Projection-based reduced basis method}\label{sec:POD-G}
Consider a nonlinear dynamic system governed by partial differential equations(PDEs):
\begin{equation}
\begin{aligned}
\mathcal{N}\left(\phi\left(\mathbf{x}\right); \pmb{\mu}\right)=0&,  \qquad \mathbf{x} \in \Omega\left(\pmb{\mu}\right)  \\
\mathcal{B}\left(\phi\left(\mathbf{x}\right); \pmb{\mu}\right)=0&,  \qquad \mathbf{x} \in \partial \Omega\left(\pmb{\mu}\right)
\end{aligned}
\label{eq_GoverningEqs}
\end{equation}
where $\mathcal{N}$ is a general nonlinear differential operator, $\phi\left(\mathbf{x}\right)$ are field variables to be solved on Cartesian coordinates $\mathbf{x}$. $\mathcal{B}$ are operators defining boundary conditions for the boundary $\partial \Omega$ of the physical  domain $\Omega$. $\pmb{\mu} \in \mathcal{P}$ are specific parameters characterizing the nonlinear dynamic system as well as the physical domain $\Omega$, where $\mathcal{P}$ is the parameter space.

As is always the case for reduced-order methods, a dynamic system is approximated by finding the its projection in a space spanned by a few well-chosen basis vectors. These basis are generated from a suitable linear combination of some precomputed high-fidelity approximations, termed as snapshots. To ensure the compatibility among snapshots, the variable physical domain has to be addressed. To this end, the variable physical domains will be mapped into a fixed computational domain with the same collation of degree of freedoms. This can be implemented by a invertible problem-dependent mapping $\mathcal{X} : \mathbf{x} \in \Omega\left(\pmb{\mu}\right) \to \pmb{ \xi} \in \widetilde \Omega$, which reads
\begin{equation}
\pmb{ \xi} = \mathcal{X} \left( \mathbf{x}; \pmb{\mu} \right),
\label{eq_Transform}
\end{equation}
and thus the governing equations (\ref{eq_GoverningEqs}) are recast as follows:
\begin{equation}
\begin{aligned}
\mathcal{N}\left(\phi\left( \mathcal{X}^{-1} \left( \pmb{ \xi}; \pmb{\mu} \right) \right); \pmb{\mu}\right)
&:=\widetilde {\mathcal{N}} \left(\phi\left( \pmb{ \xi} \right); \pmb{\mu}\right)
=0,  \qquad \pmb{ \xi} \in \widetilde \Omega
\\
\mathcal{B}\left(\phi\left(\mathcal{X}^{-1} \left( \pmb{ \xi}; \pmb{\mu} \right)\right); \pmb{\mu}\right)
&:=\widetilde {\mathcal{B}} \left(\phi\left( \pmb{ \xi} \right); \pmb{\mu}\right)
=0,  \qquad \pmb{ \xi} \in \partial \widetilde \Omega
\end{aligned}
\label{eq_GoverningEqsForXi}
\end{equation}
where $\widetilde \Omega$ is the computational domain, $\widetilde {\mathcal{B}}$ and $\widetilde {\mathcal{N}}$ are derived operators in computational space resulting from transformation Eq. (\ref{eq_Transform}).

%In this work, we are interested in finding $\phi\left(\pmb{\xi}\right)$ for a given $\pmb{\mu} \in \mathbb{P}$

\subsection{Full-order model}
To simulate the nonlinear dynamic system in Eqs. (\ref{eq_GoverningEqsForXi}), the including spatial derivatives are always first discretized by a suitable high-fidelity (HF) method (such as the pseudospectral method, spectral difference method, etc.). To achieve a satisfactory numerical accuracy, a fine mesh is employed with a large number of degrees of freedom (DOFs), generally including $N$ interior DOFs and $N_B$ boundary DOFs. Finally, the resulting discretized equations for  Eqs. (\ref{eq_GoverningEqsForXi}) are solved with a suitable explicit/implicit solver.

Here we denote the discrete solutions of Eq ( \ref{eq_GoverningEqsForXi}) in vector form $\pmb{\phi} _h \in \mathbf{R}^{N  }$ and $\pmb{\phi} _h^{B} \in \mathbf{R}^{N_B}$ for parameter $\pmb{\mu}  \in \mathcal{P}$.
Given a suitable HF method, we have the governing Eq. (\ref{eq_GoverningEqsForXi}) in discrete form
\begin{align}
\mathbf{L}_{\widetilde {\mathcal{N}}}\pmb{\phi}_h +g_{\widetilde {\mathcal{N}}}(\pmb{\phi}_h, \pmb{\phi}_h^{B})
+\mathbf{C}_{\widetilde {\mathcal{N}}}
= 0
\label{eq_DiscreteEqs}
\\
\mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\phi}_h + \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \pmb{\phi}_h^{B}
+\mathbf{C}_{\widetilde {\mathcal{B}}}
= 0
\label{eq_DiscreteBoundary}
\end{align}
where $\mathbf{L}_{\widetilde {\mathcal{N}}} \in \mathbf{R}^{N \times N}$, $\mathbf{L}_{\widetilde {\mathcal{B}}} \in \mathbf{R}^{N_B \times N}$ and $\mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \in \mathbf{R}^{N_B \times N_B}$ represent matrixes derived from linear parts of operators $\widetilde {\mathcal{N}}$ and $\widetilde {\mathcal{B}}$.
$\mathbf{C}_{\widetilde {\mathcal{N}}} \in \mathbf{R}^{N}$ and $\mathbf{C}_{\widetilde {\mathcal{B}}} \in \mathbf{R}^{N_B}$ are constant vectors independent of $\pmb{\mu}$.
$g_{\widetilde {\mathcal{N}}}: \mathbf{R}^N \times \mathbf{R}^{N_B} \mapsto \mathbf{R}^N$ is a nonlinear function derived from nonlinear part of operator $\widetilde {\mathcal{N}}$.

For the treatment of boundary conditions, it can classified into two categories, namely weakly enforced and strongly enforced boundary conditions.
As for weakly enforced boundary conditions, no DOFs are required to deploy on the boundaries, i.e. $N_B=0$, implying a vanishing of $\pmb{\phi} _h^{B}$ and also Eq. (\ref{eq_DiscreteBoundary}). As for strongly enforced boundary conditions, a suitable collocation of DOFs on boundaries is necessary. Note that the commonly used boundary conditions always linear ones, such as Dirictlet, Neumann and Robin conditions, and thus $\mathcal{B}$ are always linear operators. Without loss of generality, we restrict ourselves that the mapping in Eq. (\ref{eq_Transform}) will retain the linearity of boundary condition operator $\widetilde {\mathcal{B}}$ in computational space. Therefore, discretization of the boundary conditions result in a linear system of equations, i.e., Eq. (\ref{eq_DiscreteBoundary}).

@@

For the following simulations of flow problems, the well known $IP_N-IP_{N-2}$ method is adopted to prevent spurious pressure mode from containing the flow fields. In the $IP_N-IP_{N-2}$ method, pressure derivative is approximated without boundary points, and thus pressure is approximated with polynomial of two order lower than all other field variables, such as velocity and temperature. All other variables are discretized with Eqs. (\ref{eq_D0})-(\ref{eq_Ds}) except that the first-order difference matrix $\mathbf{D}^{1}$ of pressure is replaced with $\hat {\mathbf{D}}^1$ as follows
\begin{equation}
\left\{ \begin{aligned}
&\hat D_{i,j}^1 = 0                              & i=0,N_p \text{  or } j=0, N_p \\
&\hat D_{i,i}^1 = \frac{3\xi_i}{2(1-\xi_i^{2})}  & 1 \le i \le N_p-1\\
&\hat D_{i,j}^1 = \frac{(-1)^{i+j}(1-\xi_j^{2})}
{2(1-\xi_i^{2})(\xi_i-\xi_j)} \qquad             & 1 \le i \ne j \le N_p-1\\
\end{aligned} \right. ,
\label{eq_D1}
\end{equation}

For more details of the Chebyshev pseudospectral method, we refer the reader to the reference.

\subsection{Reduced-order model}
\label{sec_ROM}
As for solving the problem in Eq. (\ref{eq_GoverningEqsForXi}), full-order model is always suffering from large computational cost since the required degree of freedom $N$ is always very large.  Therefore, we are interested in replacing the full-order model with a well-posed  reduced-order model to represent main dynamic of the system. The full-order model is termed as reducible when Eq. (\ref{eq_FullOrderModel}) can be well approximated with $m$-dimensional subspace $\mathcal{V}=\mathbf{R}^{N \times m}$. The subspace is spanned by a suitable set of basis vectors $\{\mathbf{V}_i \in \mathbf{R}^{N} \}_{i=1}^m$.  Note that the the size of problem will be largely reduced, only if $m \ll N$. The full-order solution of the interior DOFs $\pmb{\phi} _h$ can be projected into the subspace $\mathcal{V}$
\begin{equation}
\begin{aligned}
\pmb{\phi} _h  &   =   \mathbf{V} \pmb{\alpha} + \tilde{\phi} + \pmb{\epsilon}
               &\approx \mathbf{V} \pmb{\alpha} + \tilde{\phi}
\end{aligned}
\label{eq_projection}
\end{equation}
where $\mathbf{V} \in \mathbf{R}^{N\times m}$ is a matrix with the basis vectors as its columns, $\pmb{\alpha}$ is   the coefficients of the basis, $\pmb{\epsilon}$ is the projection error, $\mathbf{I} \in \mathbf{R}^{N}$ is filled with 1.  $\tilde{\phi} \in \mathbf{R}$ is independent of $\pmb{\mu}$, set for filtering a constant value to avoid its domination on the basis, and usually it can be set as the average. The boundary conditions say that the interior DOFs have a linear relationship with interior DOFs. Thus, we can enforce the boundary conditions without any reduction. The procedure keeps the reduced-order model of high accuracy at bounaries and avoid shifting of boundary values. According to Eq.(\ref{eq_DiscreteBoundary}), the boundary DOFs can be denoted as follows
\begin{equation}
\pmb{\phi}_h^{B} = -( \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} )^{-1}
\left(
\mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\phi}_h +
\mathbf{C}_{\widetilde {\mathcal{B}}}
\right)
\label{eq_DerivePhiB}
\end{equation}

Substituting Eq. (\ref{eq_projection}) and (\ref{eq_DerivePhiB}) into Eq. (\ref{eq_DiscreteEqs}), we have the overdetermined system for interior
DOFs
\begin{equation}
\mathbf{L}_{\widetilde {\mathcal{N}}} \mathbf{V} \pmb{\alpha}
+\mathbf{g}_{\widetilde {\mathcal{N}}}
\left( \mathbf{V} \pmb{\alpha} + \tilde{\phi} + \pmb{\epsilon}, -\left( \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \right)^{-1}
\left(
\mathbf{L}_{\widetilde {\mathcal{B}}} \mathbf{V} \pmb{\alpha} +
\mathbf{C}_{\widetilde {\mathcal{B}}} + \mathbf{L}_{\widetilde {\mathcal{B}}} \mathbf{I} \tilde{\phi} + \mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\epsilon}
\right) \right)
+\mathbf{L}_{\widetilde {\mathcal{N}}} \mathbf{I} \tilde{\phi}
+\mathbf{L}_{\widetilde {\mathcal{N}}} \pmb{\epsilon}
+ \mathbf{C}_{\widetilde {\mathcal{N}}}
= 0
\label{eq_Overdetermined0}
\end{equation}
For the sake of clarity, Eq. (\ref{eq_Overdetermined0}) can be rearranged in the simplified form
\begin{equation}
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+ g         \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
= \tilde{ \pmb{\epsilon} }
\label{eq_Overdetermined1}
\end{equation}
where $\mathbf{L} \in \mathbf{R}^{N \times N}$, $\mathbf{C} \in \mathbf{R}^{N}$ and $g: \mathbf{R}^N \mapsto \mathbf{R}^N$ is the matrix, vector and function derived from Eq. (\ref{eq_Overdetermined0}), respectively.
The quantity $\tilde{ \pmb{\epsilon} }$ represent the residual resulting from the projection error $\pmb{\epsilon}$.
In the framework of a Petrov-Galerkin projection, if we consider a basis $\mathbf{W} \in \mathbf{R}^{N \times m}$ that is orthogonal to the residual,  the overdetermined system is reduced to a system of $m$ equations
\begin{equation}
\mathbf{W}^T
\left(
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+\mathbf{g} \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
\right)
=0
\label{eq_Petrov}
\end{equation}
In this work, we restrict ourself to Galerkin framework, namely $\mathbf{W}$=$\mathbf{V}$.
Thus, we have the reduced-order model as follows:
\begin{equation}
\mathbf{V}^T
\left(
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+ g         \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
\right)
=0
\label{eq_Galerkin}
\end{equation}

@@

For comparison of accuracy, the results of two analytical methods are also considered:
\begin{enumerate}[(1)]
\item \textbf{Projection}: Projection of high-fidelity solution onto reduced basis;
\item \textbf{POD-G}: The solution of the reduced-order model.
\end{enumerate}
As the PDNN is trained with the projection coefficients of high-fidelity, the PDNN targets the accuracy of the Projection. The PINN is trained to meet the reduced-order model, the PINN targets the accuracy the POD-G. The PRNN can be viewed as a blending of the PDNN and PINN, and thus its accuracy is expected to fall somewhere between those of the Projection and POD-G.

@@

Note that the Projection, POD-G, PDNN, PINN and PRNN methods are all coded in Python. The networks built are are all under the framework of Pytorch. The training of networks are all  implemented on two GUPs (NVIDIA Quadro GP100) of a server class station. To solve the reduced-order model directly for POD-G, the nonlinear solver "linalg.solve" in  Numpy library is employed. We refer the reader to the repository \footnote{available at \url{https://github.com/cwq2016/POD-PINN}} for further details of the code method. For different data set as discussed above, we employ the specific sampling methods in parameter space: for building the RB, we adopt the Sobol sequences, a quasi-random low-discrepancy sequences; For choosing residual points, we use the Latin hypercube sampling; For generating test data set, we employ uniformly tensor-product grid.

@@

%% References
\bibliographystyle{elsarticle-num}
\bibliography{ref}

>>>>

%% main text
\section{Introduction}
In recent years, although high-fidelity numerical method has witnessed substantial developments for modeling complex phenomena, it is still challenging for many applications, such as design, optimization, control and uncertainty quantification problems. Such applications are governed by parameterized partial differential equations(PDEs) \cite{hesthaven2016certified, quarteroni2015reduced}, where parameters characterize underlying geometry, boundary conditions, source terms and physical properties, etc. High-fidelity numerical method are prohibitively expensive to such applications in multi-entry and real-time contexts, due to the required lots of degrees of freedom(DOFs).
%Although increasing computational power and parallel techniques are nowadays available to largely reduce the consumed wall time, the total cost with respect to both consumed CPU time and money remains prohibitively expensive.
The need to largely reduce computational cost gives birth to reduced-order methods \cite{lucia2004reduced}, aiming at replacing the full-order system with a cheap reduced-order system with an affordable loss of accuracy.

Reduced basis (RB) method is one of the well-known and widely-used reduced-order methods, and always follows the offline-online paradigm \cite{maday2006reduced}. The offline stage comprises preparing the high-fidelity solutions(snapshots), extracting the reduced basis and building the cheap evaluation model. The reduced space, spanned by the reduced basis  extracted from the snapshots, is expected to represent the main dynamics of the full-order model. There exist many methods to extract the reduced basis, such as the Proper Orthogonal Decomposition (POD) \cite{hesthaven2016certified,liang2002proper,quarteroni2015reduced}, the  Proper Generalized Decomposition \cite{chinesta2011short}, the Piecewise Tangential Interpolation \cite{gallivan2002model}, the Matrix Interpolation \cite{panzer2010parametric}, the Loewner framework and several greedy-based approaches for the identification of sub-optimal subspaces \cite{billaud2017dynamical, lappano2016greedy, hesthaven2014efficient}. Among them, the POD perhaps is the most widely-known and widely-used one, where the reduced basis is generated by a singular value decomposition (SVD) algorithm for some given snapshots with respect to a chosen set of parameters. After the reduced basis has been properly set up, an approximation to high-fidelity solution is recovered from projection coefficients of the reduced space. Then a suitable model will be built offline, aiming to provide online evaluation for a new given parameter.
For building such a model, both 'white-box' and 'black-box' strategies are applied in the literature.

Galerkin method \cite{rowley2004model, wang2020recurrent, deane1991low} is one of widely-used white-box strategies. In the offline stage,
a reduced-order model determining the reduced basis coefficients is derived from Galerkin projection of the full-order model. In the online stage, the reduced-order model is solved by a suitable numerical solver for each parameter.
As RB coefficients is directly solved by a deterministic method, the achieved approximation accuracy is always very good.
However, the online solving of the reduced-order model is not trivial, which remains an open problem with respect to its stability, accuracy and convergence \cite{huang2018challenges, iollo2000stability, rowley2004model}. Besides, the online solving of the reduced-order model is still time consuming especially for complex nonlinear problems, even if it is very cheap compared with the solving of full-order model.

%Many works have been devoted to improve the stability and accuracy, such as the structure-preservation, supremizer enrichment,basis adaption, L1-norm minimization, and least-squares. Petrov-Galerkin (LSPG) technique.

The 'black-box' strategy is also termed as an non-intrusive procedure, in which the building and also the solving of reduced-order model is avoided. Usually, the high-fidelity simulations produce snapshots are treated as a black-box.
a mapping from parameters to projection coefficients is build in a data-driven way. During the offline stage, a map between the parameter values and the projection coefficients is built by trained a data-driven model. During the online stage, the projection coefficients for new parameter values can be recovered as outputs of the data-driven model.  For example, non-intrusive approaches using radial basis function (RBF) \cite{chen2018greedy, walton2013reduced, xiao2015non}, artificial neural network(ANN) \cite{hesthaven2018non} and Gaussion process regression(GPR) \cite{guo2019data} have been applied successively for parameterized partial differential equations, even for flow problems of strong nonlinearity. These approaches benefit from their high established effectiveness and efficient online evaluation. However, the drawback, common for data-driven model, is their requirement for an excessive number of observed data to guarantee accuracy. That is to say, many high-fidelity solutions has to be precomputed,  sometimes leading to an unacceptable cost even if it is performed in the offline stage \cite{hesthaven2018non}.

In this work, we try to take the advantages of the above two strategies to build the cheap evaluation model, namely the high accuracy of the POD-G and the effectiveness of  data-driven model. POD-G targets the full-order model, while the data-driven models target high-fidelity solutions. These two strategies all aimed at finding an approximation but in different directions.
We keep on the intrusive approach and utilize the reduced-order information to build an approximation model. Inspired by the well-know physics-informed neural network (PINN) \cite{raissi2019physics, raissi2020hidden, mao2020physics}, we can directly solve the reduced-order model by  optimizing a neural network. For the PINN approach, there is no need for labeled data, thus no need for extra snapshots, and what we need to do is to train a network to satisfy the reduced-order model in some sense. Besides this approach, the projection coefficients of each snapshot can also be added into the training of network, although they are not the solutions of the reduced-order model. we term this approach as the physics-reinforced network (PRNN). As blending strategies, both PINN and PRNN promise enjoy a higher accuracy and effectiveness for nonlinear parameterized PDEs. To test assertion, the PINN and PRNN are applied to one-dimenisonal Burges' equation, two-dimensional lid-driven flow and natural convection in enclosure. A detailed comparison with the white-box POD-G method and POD-NN method proposed by Jan \cite{hesthaven2018non} is analysed for the three test cases.

The remainder of this paper is organized as follows. Section 2 presents the framework from parameterized PDEs to the reduced-order model. Section 3 briefly introduce the POD-NN method (refered to PDNN in this work) and presents the derivation of PINN and PRNN method, based on the reduced-order information. Section 4 details some numerical setups for the methods. some numerical results to show the superiority of the proposed methods, In Section 5, some conclusions are given.

\section{Projection-based reduced basis method}\label{sec:POD-G}
Consider a nonlinear dynamic system governed by the following parameterized partial differential equations(PDEs):
\begin{equation}
\begin{aligned}
\mathcal{N}\left(\phi\left(\mathbf{x}\right); \pmb{\mu}\right)=0&,  \qquad \mathbf{x} \in \Omega\left(\pmb{\mu}\right)  \\
\mathcal{B}\left(\phi\left(\mathbf{x}\right); \pmb{\mu}\right)=0&,  \qquad \mathbf{x} \in \partial \Omega\left(\pmb{\mu}\right)
\end{aligned}
\label{eq_GoverningEqs}
\end{equation}
where $\mathcal{N}$ is a general nonlinear differential operator, $\phi\left(\mathbf{x}\right)$ are field variables to be solved on Cartesian coordinates $\mathbf{x}$. $\mathcal{B}$ are operators defining boundary conditions for the boundary $\partial \Omega$ of the physical  domain $\Omega$. $\pmb{\mu} \in \mathcal{P}$ are specific parameters characterizing the nonlinear dynamic system as well as the physical domain $\Omega$, where $\mathcal{P}$ is the parameter space.

As is always the case for reduced-order methods, a dynamic system is approximated by finding the its projection in a space spanned by a few well-chosen basis vectors. These basis are generated from a suitable linear combination of some precomputed high-fidelity approximations, termed as snapshots. To ensure the compatibility among snapshots, the variable physical domain has to be addressed. To this end, the variable physical domain will be mapped into a fixed computational domain with the same collation of degrees of freedom. This can be implemented by an invertible problem-dependent mapping $\mathcal{X} : \mathbf{x} \in \Omega\left(\pmb{\mu}\right) \to \pmb{ \xi} \in \widetilde \Omega$, which reads
\begin{equation}
\pmb{ \xi} = \mathcal{X} \left( \mathbf{x}; \pmb{\mu} \right),
\label{eq_Transform}
\end{equation}
and thus the governing equations (\ref{eq_GoverningEqs}) are recast as follows:
\begin{equation}
\begin{aligned}
\mathcal{N}\left(\phi\left( \mathcal{X}^{-1} \left( \pmb{ \xi}; \pmb{\mu} \right) \right); \pmb{\mu}\right)
&:=\widetilde {\mathcal{N}} \left(\phi\left( \pmb{ \xi} \right); \pmb{\mu}\right)
=0,  \qquad \pmb{ \xi} \in \widetilde \Omega
\\
\mathcal{B}\left(\phi\left(\mathcal{X}^{-1} \left( \pmb{ \xi}; \pmb{\mu} \right)\right); \pmb{\mu}\right)
&:=\widetilde {\mathcal{B}} \left(\phi\left( \pmb{ \xi} \right); \pmb{\mu}\right)
=0,  \qquad \pmb{ \xi} \in \partial \widetilde \Omega
\end{aligned}
\label{eq_GoverningEqsForXi}
\end{equation}
where $\widetilde \Omega$ is the computational domain, $\widetilde {\mathcal{B}}$ and $\widetilde {\mathcal{N}}$ are the derived operators in computational space resulting from the transformation Eq. (\ref{eq_Transform}).

\subsection{Full-order model}
To simulate the nonlinear dynamic system in Eqs. (\ref{eq_GoverningEqsForXi}), the including spatial derivatives are always first discretized by a suitable high-fidelity (HF) method (such as the Chebyshev pseudospectral method \cite{chen2018multidomain, chen2020parallel}, spectral difference method \cite{chen2020collocated}, etc.). To achieve a satisfactory numerical accuracy, a fine mesh is employed with a large number of degrees of freedom (DOFs), generally including $N$ interior DOFs and $N_B$ boundary DOFs. Finally, the resulting discretized equations for  Eqs. (\ref{eq_GoverningEqsForXi}) are solved with a suitable explicit/implicit solver.

Here we denote the discrete solutions of Eq ( \ref{eq_GoverningEqsForXi}) in vector form $\pmb{\phi} _h \in \mathbf{R}^{N  }$ and $\pmb{\phi} _h^{B} \in \mathbf{R}^{N_B}$ for parameter $\pmb{\mu}  \in \mathcal{P}$.
Given a suitable HF method, we have the governing Eq. (\ref{eq_GoverningEqsForXi}) in discrete form
\begin{align}
\mathbf{L}_{\widetilde {\mathcal{N}}}\pmb{\phi}_h +g_{\widetilde {\mathcal{N}}}(\pmb{\phi}_h, \pmb{\phi}_h^{B})
+\mathbf{C}_{\widetilde {\mathcal{N}}}
= 0
\label{eq_DiscreteEqs}
\\
\mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\phi}_h + \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \pmb{\phi}_h^{B}
+\mathbf{C}_{\widetilde {\mathcal{B}}}
= 0
\label{eq_DiscreteBoundary}
\end{align}
where $\mathbf{L}_{\widetilde {\mathcal{N}}} \in \mathbf{R}^{N \times N}$, $\mathbf{L}_{\widetilde {\mathcal{B}}} \in \mathbf{R}^{N_B \times N}$ and $\mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \in \mathbf{R}^{N_B \times N_B}$ represent matrixes derived from linear parts of operators $\widetilde {\mathcal{N}}$ and $\widetilde {\mathcal{B}}$.
$\mathbf{C}_{\widetilde {\mathcal{N}}} \in \mathbf{R}^{N}$ and $\mathbf{C}_{\widetilde {\mathcal{B}}} \in \mathbf{R}^{N_B}$ are constant vectors independent of $\pmb{\phi} _h$.
$g_{\widetilde {\mathcal{N}}}: \mathbf{R}^N \times \mathbf{R}^{N_B} \mapsto \mathbf{R}^N$ is a nonlinear function derived from the nonlinear part of operator $\widetilde {\mathcal{N}}$.

For the treatment of boundary conditions, it can be classified into two categories, namely weakly enforced and strongly enforced boundary conditions.
As for weakly enforced boundary conditions, no DOFs is required to deploy on the boundaries, i.e. $N_B=0$, implying a vanishing of $\pmb{\phi} _h^{B}$ and also Eq. (\ref{eq_DiscreteBoundary}). As for strongly enforced boundary conditions, a suitable collocation of DOFs on boundaries is necessary. Note that the commonly used boundary conditions always linear ones, such as Dirictlet, Neumann and Robin conditions, and thus $\mathcal{B}$ are always linear operators. Without loss of generality, we restrict ourselves that the mapping in Eq. (\ref{eq_Transform}) will retain the linearity of boundary condition operator $\widetilde {\mathcal{B}}$ in computational space. Therefore, discretization of the boundary conditions result in a linear system of equations, i.e., Eq. (\ref{eq_DiscreteBoundary}).

@@

For the following simulations of flow problems, the well known $IP_N-IP_{N-2}$ method \cite{zhang2010explicit} is adopted to prevent spurious pressure mode from
contaminating the flow fields \cite{peyret2013spectral}. In the $IP_N-IP_{N-2}$ method, pressure derivative is approximated without pressure values at boundary points, and thus pressure is approximated with polynomial of two order lower than all other field variables, such as velocity and temperature. All other variables are discretized with Eqs. (\ref{eq_D0})-(\ref{eq_Ds}) except that the first-order difference matrix $\mathbf{D}^{1}$ of pressure is replaced with $\hat {\mathbf{D}}^1$ as follows
\begin{equation}
\left\{ \begin{aligned}
&\hat D_{i,j}^1 = 0                              & i=0,N_p \text{  or } j=0, N_p \\
&\hat D_{i,i}^1 = \frac{3\xi_i}{2(1-\xi_i^{2})}  & 1 \le i \le N_p-1\\
&\hat D_{i,j}^1 = \frac{(-1)^{i+j}(1-\xi_j^{2})}
{2(1-\xi_i^{2})(\xi_i-\xi_j)} \qquad             & 1 \le i \ne j \le N_p-1\\
\end{aligned} \right. ,
\label{eq_D1}
\end{equation}

For more details of the Chebyshev pseudospectral method, we refer the reader to the reference \cite{peyret2013spectral, chen2018multidomain, chen2020parallel}.

\subsection{Reduced-order model}
\label{sec_ROM}
As for solving the problem in Eq. (\ref{eq_GoverningEqsForXi}), full-order model is always suffering from large computational cost since the required degrees of freedom $N$ is always very large.  Therefore, we are interested in replacing the full-order model with a well-posed  reduced-order model to represent main dynamic of the system. The full-order model is termed as reducible when high-fidelity solution $\pmb{\phi} _h$ can be well approximated in $m$-dimensional subspace $\mathcal{V}=\mathbf{R}^{N \times m}$. The subspace is spanned by a suitable set of basis vectors $\{\mathbf{V}_i \in \mathbf{R}^{N} \}_{i=1}^m$.  Note that the the size of problem will be largely reduced, only if $m \ll N$. The full-order solution of the interior DOFs $\pmb{\phi} _h$ can be projected into the subspace $\mathcal{V}$
\begin{equation}
\begin{aligned}
\pmb{\phi} _h  &   =   \mathbf{V} \pmb{\alpha} + \tilde{\phi} + \pmb{\epsilon}
               &\approx \mathbf{V} \pmb{\alpha} + \tilde{\phi}
\end{aligned}
\label{eq_projection}
\end{equation}
where $\mathbf{V} \in \mathbf{R}^{N\times m}$ is a matrix with the basis vectors as its columns, $\pmb{\alpha}$ is   the coefficients of the basis, $\pmb{\epsilon}$ is the projection error.  $\tilde{\phi} \in \mathbf{R}$ is independent of $\pmb{\mu}$, set for filtering a constant value to avoid its domination on the basis, and usually it can be set as the average. The boundary conditions in Eq. (\ref{eq_DiscreteBoundary}) say that the interior DOFs have a linear relationship with interior DOFs. Thus, we can enforce the boundary conditions without any reduction. The procedure keeps the reduced-order model of high accuracy at bounaries and avoid shifting of boundary values. According to Eq.(\ref{eq_DiscreteBoundary}), the boundary DOFs can be denoted as follows
\begin{equation}
\pmb{\phi}_h^{B} = -( \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} )^{-1}
\left(
\mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\phi}_h +
\mathbf{C}_{\widetilde {\mathcal{B}}}
\right)
\label{eq_DerivePhiB}
\end{equation}

Substituting Eq. (\ref{eq_projection}) and (\ref{eq_DerivePhiB}) into Eq. (\ref{eq_DiscreteEqs}), we have the overdetermined system for interior
DOFs
\begin{equation}
\mathbf{L}_{\widetilde {\mathcal{N}}} \mathbf{V} \pmb{\alpha}
+\mathbf{g}_{\widetilde {\mathcal{N}}}
\left( \mathbf{V} \pmb{\alpha} + \tilde{\phi} + \pmb{\epsilon}, -\left( \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \right)^{-1}
\left(
\mathbf{L}_{\widetilde {\mathcal{B}}} \mathbf{V} \pmb{\alpha} +
\mathbf{C}_{\widetilde {\mathcal{B}}} + \mathbf{L}_{\widetilde {\mathcal{B}}} \mathbf{I} \tilde{\phi} + \mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\epsilon}
\right) \right)
+\mathbf{L}_{\widetilde {\mathcal{N}}} \mathbf{I} \tilde{\phi}
+\mathbf{L}_{\widetilde {\mathcal{N}}} \pmb{\epsilon}
+ \mathbf{C}_{\widetilde {\mathcal{N}}}
= 0
\label{eq_Overdetermined0}
\end{equation}
where $\mathbf{I} \in \mathbf{R}^{N}$ is an vector filled with 1. For the sake of clarity, Eq. (\ref{eq_Overdetermined0}) can be rearranged in the simplified form
\begin{equation}
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+ g         \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
= \tilde{ \pmb{\epsilon} }
\label{eq_Overdetermined1}
\end{equation}
where $\mathbf{L} \in \mathbf{R}^{N \times N}$, $\mathbf{C} \in \mathbf{R}^{N}$ and $g: \mathbf{R}^N \mapsto \mathbf{R}^N$ is the matrix, vector and function derived from Eq. (\ref{eq_Overdetermined0}), respectively.
The quantity $\tilde{ \pmb{\epsilon} }$ represent the residual resulting from the projection error $\pmb{\epsilon}$.
In the framework of Petrov-Galerkin projection, if we consider a basis $\mathbf{W} \in \mathbf{R}^{N \times m}$ that is orthogonal to the residual,  the overdetermined system is reduced to a system of $m$ equations
\begin{equation}
\mathbf{W}^T
\left(
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+\mathbf{g} \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
\right)
=0
\label{eq_Petrov}
\end{equation}
In this work, we restrict ourself to Galerkin framework, namely $\mathbf{W}$=$\mathbf{V}$.
Thus, we have the reduced-order model as follows:
\begin{equation}
\mathbf{V}^T
\left(
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+ g         \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
\right)
=0
\label{eq_Galerkin}
\end{equation}

@@

For comparison of accuracy, the results of two analytical methods are also considered:
\begin{enumerate}[(1)]
\item \textbf{Projection}: Projection of high-fidelity solution onto reduced basis;
\item \textbf{POD-G}: The solution of the reduced-order model.
\end{enumerate}
As the PDNN is trained with the projection coefficients of high-fidelity solutions, the PDNN targets the accuracy of the Projection. The PINN is trained to meet the reduced-order model, the PINN targets the accuracy of the POD-G. The PRNN can be viewed as a blending of the PDNN and PINN, and thus its accuracy is expected to fall somewhere between those of the Projection and POD-G.

@@

Note that the Projection, POD-G, PDNN, PINN and PRNN methods are all coded in Python. The networks built are all under the framework of Pytorch. The training of networks are all  implemented on two GUPs (NVIDIA Quadro GP100) of a server class station. To solve the reduced-order model directly for POD-G, the nonlinear solver "linalg.solve" in  Numpy library is employed. We refer the reader to the repository \footnote{available at \url{https://github.com/cwq2016/POD-PINN}} for further details of the code. For different data set as discussed above, we employ the specific sampling methods in parameter space: for building the RB, we adopt the Sobol sequences, a quasi-random low-discrepancy sequences; For choosing residual points, we use the Latin hypercube sampling; For generating test data set, we employ uniformly tensor-product grid.

@@

%% References
\section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{ref}
